The Title Goes Here with Each Initial Letter Capitalized

### 2025-02-04 uca_radio_eclipse_jurpa.tex
Updating author names.
I'm adding our names and affiliation.

The affiliation is screwed up in the output PDF because of a quirk
with the way that the AIP template handles commas in the affiliation
field, but that's hopefully something we don't have to mess with.
They can fix that when they typeset the thing for publication.

\title{The Title Goes Here with Each Initial Letter Capitalized}% Force line breaks with \\

\author{Author's Name} % Write as First name Surname
 \email[Corresponding author: ]{first.author@insitution.edu}
\author{Author's Name}%
 \email{second.author@institution.edu.}
\affiliation{
  Replace this text with an author's affiliation
  (use complete addresses, including country name or code).% Force line breaks with \\ if necessary
}

\author{Another's Name}
 \email{third.author@anotherinstitution.edu}
\affiliation{%
Second institution and/or address% Force line breaks with \\ if necessary
}%
\affiliation{You would list an author's second affiliation (if applicable) here.}

>>>>

\title{}% Force line breaks with \\

\author{August Childress} % Write as First name Surname
\email[Corresponding author: ]{achildress@cub.uca.edu}
\affiliation{Department of Physics, Astronomy, and Engineering, University of Central Arkansas, Conway, AR 72035, USA}
\author{Blayne Griffin}%
\email{bgriffin@cub.uca.edu.}
\affiliation{Department of Physics, Astronomy, and Engineering, University of Central Arkansas, Conway, AR 72035, USA}
\author{Jeremy Lusk}
\email{jlusk@uca.edu}
\affiliation{Department of Physics, Astronomy, and Engineering, University of Central Arkansas, Conway, AR 72035, USA}
